---
title: "Creating Tables and Plots for Deans"
author: "Spiro Stilianoudakis"
date: "September 18, 2018"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```


```{r}
library(ggplot2)
library(DT)
library(knitr)
```

# Dean Survey

```{r}
setwd("C:/Users/Spiro Stilianoudakis/Documents/Dentistry_VCU_RA_2018/Holtz_Lena")

deans <- readRDS("deans.rds")

cguidedf  <- readRDS("cguidedf.rds")

ctraindf <- readRDS("ctraindf.rds")

dideddf <- readRDS("dideddf.rds")

tformatdf <- readRDS("tformatdf.rds")

```


## School Region

###What is the region of your dental school?

```{r}
region <- data.frame(table(deans$region_school, useNA = "ifany"))
names(region) <- c("Region", "Count")

p<-ggplot(data=region, aes(x = Region, y = Count)) +
  ylim(0,8) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() #+
  #coord_flip()
p

```


## Position
###What is your position?

```{r}

position <- data.frame(table(deans$position, useNA = "ifany"))
names(position) <- c("Position", "Count")

p<-ggplot(data=position, aes(x = Position, y = Count)) +
  ylim(0,9) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() #+
  #coord_flip()
p

pos2 <- deans[,names(deans) %in% c("position", "other_position")]
pos2.1 <- data.frame(Position = sort(rep(unique(pos2$position),3)),
                     "Other Position" = rep(unique(pos2$other_position),3),
                     Count = c(3,0,0,8,0,0,0,4,3))

pos2.1$Other.Position <- as.character(pos2.1$Other.Position)
pos2.1$Other.Position[which(pos2.1$Other.Position=="Director")] <- "Program Director"
pos2.1$Other.Position <- factor(pos2.1$Other.Position)

p <- ggplot(data=pos2.1, aes(x=Position, y=Count, fill=Other.Position)) +
  geom_bar(stat="identity") +
  scale_fill_manual(name = "Other Position", 
                    breaks = c("Program Director", "Professor"),
                    values=c("green","red","steelblue")) +
  #geom_text(aes(label=Count), vjust=-.5, color="white", size=5)+
  theme_minimal()
p

```


## Department Chair
###Which department do you chair?

```{r}
deptchair <- data.frame(table(deans$dept_chair, useNA = "ifany"))
names(deptchair) <- c("Department", "Count")
deptchair$Department <- as.character(deptchair$Department)
deptchair$Department[1] <- "Clinical Sciences"
deptchair$Department[7] <- "Clinical Sciences"
deptchair$Department[2] <- "Comprehensive Dentistry"

deptchair$Count[1] <- 2
deptchair$Count[2] <- 2

deptchair <- deptchair[c(1,2,4,5,6),]

p<-ggplot(data=deptchair, aes(x = Department, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,3) +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 25))) #+
  #coord_flip()
p

```

## Age
###What is your age?

```{r}
#summary(deans$age)

age <- data.frame(Minimum = as.vector(summary(deans$age))[1],
                  "First Quartile"= as.vector(summary(deans$age))[2],
                  Median= as.vector(summary(deans$age))[3],
                  Mean= as.vector(summary(deans$age))[4],
                  "Third Quartile"= as.vector(summary(deans$age))[5],
                  Maximum= as.vector(summary(deans$age))[6])
age <- round(age, 2)
#datatable(age)
kable(age)

```

## Gender
###What is your gender?

```{r}
gender <- data.frame(table(deans$gender, useNA = "ifany"))
names(gender) <- c("Gender", "Count")

p<-ggplot(data=gender, aes(x = Gender, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,11) +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 20))) #+
  #coord_flip()
p
```

## Established Guidlines
###Do you currently have established clinical guidelines for antibiotic prescribing within any disciplines/departments at your dental school?

```{r}

guides <- data.frame(table(deans$established_guidelines, useNA = "ifany"))
names(guides) <- c("Established.Guidelines", "Count")

p<-ggplot(data=guides, aes(x = Established.Guidelines, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,13) +
  scale_x_discrete(name = "Established Guidelines") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() #+
  #theme(axis.text.x = element_text(angle = 90)) #+
  #coord_flip()
p

```

## Department Guidelines
###Which disciplines have established clinical guidelines for antibiotic prescribing?

```{r}
#cguidedf

p<-ggplot(data=cguidedf, aes(x = Discipline, y = Established.Guidlines)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,7) +
  scale_x_discrete(name = "Discipline") +
  ylab("Count") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Established.Guidlines), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 20))) #+
  #coord_flip()
p



```

## Courses
###Which courses currently provide didactic education regarding antibiotics in the dental school curriculum?

```{r}
#dideddf
dideddf <- dideddf[-9,]

p<-ggplot(data=dideddf, aes(x = Department, y = Didactic.Education)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,20) +
  scale_x_discrete(name = "Department") +
  ylab("Count") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Didactic.Education), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p

#kable(deans$other_courses)


```

## Rate education
### How would you rate the education regarding appropriate use of antibiotics in the dental school curriculum?

```{r}
ed <- data.frame(table(deans$rate_education, useNA = "ifany"))
names(ed) <- c("Rating", "Count")

p<-ggplot(data=ed, aes(x = Rating, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,11) +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p
```

## Hours didactic
###How many hours of training in principles and indications of antibiotic use do the dental students receive during their 4 years of study?

```{r}
hours <- data.frame(table(deans$hours_didactic, useNA = "ifany"))
names(hours) <- c("Hours", "Count")

p<-ggplot(data=hours, aes(x = Hours, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,11) +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p
```

## Format helpful
###Which of the teaching formats do you think have been most helpful in the education of dental students regarding antibiotics? [Please select up to 3]

```{r}
#tformatdf
tformatdf <- tformatdf[-8,]

p<-ggplot(data=tformatdf, aes(x = Teaching.Format, y = Most.Helpful)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,19) +
  scale_x_discrete(name = "Teaching Format") +
  ylab("Count") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Most.Helpful), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 50))) #+
  #coord_flip()
p

```

## Resistance curriculum
###Is antimicrobial resistance currently being taught in the dental school curriculum?

```{r}

#table(deans$resistance_curriculum)

curr <- data.frame(table(deans$resistance_curriculum, useNA = "ifany"))
names(curr) <- c("Curriculum", "Count")

p<-ggplot(data=curr, aes(x = Curriculum, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,18) +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p

```

## Clinical training
###Which departments/disciplines currently provide clinical training regarding antibiotics within the dental school curriculum?

```{r}
#ctraindf
ctraindf <- ctraindf[-9,]

p<-ggplot(data=ctraindf, aes(x = Department, y = Clinical.Training)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,19) +
  scale_x_discrete(name = "Teaching Format") +
  ylab("Count") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Clinical.Training), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 20))) #+
  #coord_flip()
p
```


## Students benefit
###Do you think students could benefit from more education on antibiotic selection and indications at your dental school?

```{r}
#table(deans$students_benefit)

sben <- data.frame(table(deans$students_benefit, useNA = "ifany"))
names(sben) <- c("Benefit.to.Student", "Count")
sben$Benefit.to.Student <- factor(sben$Benefit.to.Student, levels=c("Yes", "No", "Recieving adequate training"))

p<-ggplot(data=sben, aes(x = Benefit.to.Student, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,11) +
  scale_x_discrete(name = "Benefit to Student") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 25))) #+
  #coord_flip()
p
```


## Protocols
###Are there any antibiotic stewardship/monitoring protocols in place at your institution?

```{r}
#table(deans$protocols)

pro <- data.frame(table(deans$protocols, useNA = "ifany"))
names(pro) <- c("Protocols", "Count")
pro$Protocols <- factor(pro$Protocols, levels=c("Yes", "No", "Unsure"))

p<-ggplot(data=pro, aes(x = Protocols, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,11) +
  scale_x_discrete(name = "Protocols") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p
```

## Percieved importances
###On a scale of 0-10, how important do you perceive this topic to be within the dental curriculum? Note: 0 being least important and 10 being most important

```{r}
#table(deans$perceived_importances)

imp <- data.frame(table(deans$perceived_importances, useNA = "ifany"))
names(imp) <- c("Importance", "Count")
imp <- rbind(data.frame(Importance=0,Count=0), imp)
imp$Importance <- factor(imp$Importance, levels=0:10)
#imp$Importance <- factor(imp$Importance, levels=c())

p<-ggplot(data=imp, aes(x = Importance, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,7) +
  scale_x_discrete(name = "Importance") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() #+
  #theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p
```


## Rate unnecessary
###What percentage of antibiotic prescriptions within dentistry do you think are found to be unnecessary or inappropriate?

```{r}
#table(deans$rate_unnecessary)

unnec <- data.frame(table(deans$rate_unnecessary, useNA = "ifany"))
names(unnec) <- c("Percentage", "Count")
unnec <- rbind.data.frame(unnec, data.frame(Percentage="61-80%", Count=0))
unnec <- unnec[c(1,2,3,4,6,5),]
unnec$Percentage <- as.character(unnec$Percentage)
unnec$Percentage <- factor(unnec$Percentage)
levels(unnec$Percentage) <- c("<1%"  , "1-20%",  "21-40%",  "41-60%","61-80%", "81-100%")

p<-ggplot(data=unnec, aes(x = Percentage, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,8) +
  scale_x_discrete(name = "Percentage") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p
```


## Dentistry role
###Do you feel that the field of dentistry should play an important role in reducing antimicrobial resistance?

```{r}
#table(deans$dentistry_role)

drole <- data.frame(table(deans$dentistry_role, useNA = "ifany"))
names(drole) <- c("Role", "Count")
#drole$Role <- factor(unnec$Percentage, levels=c(Strongly Agree             Agree           Neutral          Disagree Strongly Disagree ))

p<-ggplot(data=drole, aes(x = Role, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,13) +
  scale_x_discrete(name = "") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p
```


## Students role
###Do you feel that dental students can contribute in reducing/controlling antibiotic resistance?

```{r}
#table(deans$students_role)

srole <- data.frame(table(deans$students_role, useNA = "ifany"))
names(srole) <- c("Role", "Count")
#drole$Role <- factor(unnec$Percentage, levels=c(Strongly Agree             Agree           Neutral          Disagree Strongly Disagree ))

p<-ggplot(data=srole, aes(x = Role, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  ylim(0,11) +
  scale_x_discrete(name = "") +
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p
```


