---
title: "Creating Tables and Plots for Students"
author: "Spiro Stilianoudakis"
date: "September 24, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```


```{r}
library(ggplot2)
library(DT)
library(knitr)
```

# Student Survey

```{r}
setwd("Y:/Oral Health Services Research Core/Spiro/Holtz_Lena")

students <- readRDS("students.rds")

#removing students that didn't answer specific questions
vars <- c("record_id","infection","choosing","dose","duration","demand","should_role", "percent_unnecessary", "more_educ","num_rx","broad_spec","long_duration","dose_low","livestock","hand_wash","development","not_warranted","diagnostic_tools","wrong_anti","non_compliance", "age")

students <- students[complete.cases(students[,which(names(students) %in% vars)]),]

dim(students) 

saveRDS(students, "students.rds")

```

## Year of Dental School

### What year of dental school are you in?

```{r}
year <- data.frame(table(students$year_school, useNA = "ifany"))

p<-ggplot(data=year, aes(x = Var1, y = Freq)) +
  #ylim(0,8) +
  ylab("Count") +
  xlab("Year of Dental School") +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Freq), vjust=-.5, color="black", size=5)+
  scale_x_discrete(labels=c("3rd", "4th"))+
  theme_minimal() #+
  #coord_flip()
p


```

## School Region

###What is the region of your dental school?

```{r}
region <- data.frame(table(students$region, useNA = "ifany"))
names(region) <- c("Region", "Count")

p<-ggplot(data=region, aes(x = Region, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  scale_x_discrete(labels=c("Northeast",
                            "South",
                            "Midwest",
                            "West"))+
  theme_minimal() #+
  #coord_flip()
p

```


## Age
###What is your age?

```{r}
#summary(students$age)

age <- data.frame(Minimum = as.vector(summary(students$age))[1],
                  "First Quartile"= as.vector(summary(students$age))[2],
                  Median= as.vector(summary(students$age))[3],
                  Mean= as.vector(summary(students$age))[4],
                  SD=sd(na.omit(students$age)),
                  "Third Quartile"= as.vector(summary(students$age))[5],
                  Maximum= as.vector(summary(students$age))[6],
                  Missing=length(which(is.na(students$age))))
age <- round(age, 2)
#datatable(age)
kable(age)

```


## Gender
###What is your gender?

```{r}
gender <- data.frame(table(students$gender, useNA = "ifany"))
names(gender) <- c("Gender", "Count")

p<-ggplot(data=gender, aes(x = Gender, y = Count)) +
  ylim(0,115) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("Male",
                            "Female"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 20))) #+
  #coord_flip()
p
```

##Plans
###What are your plans following graduation?

```{r}
plans <- data.frame(table(students$plans, useNA = "ifany"))

p<-ggplot(data=plans, aes(x = Var1, y = Freq)) +
  ylim(0,82) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  ylab("Count")+
  xlab("Career")+ 
  geom_text(aes(label=Freq), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("Private Practice",
                            "Academia",
                            "Public Practice",
                            "Corporate Practice",
                            "Residency",
                            "Other"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 20))) #+
  #coord_flip()
p

```

##Residency
###Which residency are you most interested in

```{r}

residency <- data.frame(table(students$residency, useNA = "always"))

p<-ggplot(data=residency, aes(x = stringr::str_wrap(Var1, 10), y = Freq)) +
  #ylim(0,26) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  ylab("Count")+
  xlab("Career")+ 
  geom_text(aes(label=Freq), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("Advanced Ed in Gen Dentistry",
                            #"Dental Public Health",
                            "Endodontics",
                            "General Practice Residency",
                            #"Oral & Maxillofacial Radiology",
                            "Oral & Maxillofacial Surgery",
                            #"Oral & Maxillofacial Pathology",
                            "Orthodontics",
                            "Pediatric Dentistry",
                            "Periodontics",
                            "Prosthodontics",
                            "Unknown"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 50))) #+
  #coord_flip()
p

```


##rate_curriculum
###How would you rate your dental education regarding appropriate use of antibiotics so far in your dental school curriculum?

```{r}

curriculum <- data.frame(table(students$rate_curriculum, useNA = "ifany"))
curriculum$Var1 <- as.numeric(as.character(curriculum$Var1))
curriculum <- curriculum[order(curriculum$Var1, decreasing = TRUE),]
curriculum$Var1 <- factor(curriculum$Var1, levels = c("2", "1", "0", "-1", "-2"))


p<-ggplot(data=curriculum, aes(x = Var1, y = Freq)) +
  ylim(0,101) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  ylab("Count")+
  xlab("Rating")+ 
  geom_text(aes(label=Freq), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("Very useful",
                            "Useful",
                            "Neutral",
                            "Not useful",
                            "Not at all useful"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 20))) #+
  #coord_flip()
p

```

##Department Courses
###Which department/courses do you feel you have gained the majority of your decision-making skills and knowledge regarding antibiotic prescribing practices? [Please select up to 3]

```{r}
courses <- students[,grep("dept_courses___",names(students))]
courses <- courses[,1:9]
courses <- data.frame(colSums(courses))

p<-ggplot(data=courses, aes(x = rownames(courses), y = colSums.courses.)) +
  ylim(0,135) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  ylab("Count")+
  xlab("Department")+ 
  geom_text(aes(label=colSums.courses.), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("Community Dentistry",
                            "Endodontics",
                            "Epidemiology",
                            "Microbiology",
                            "Periodontics",
                            "Pharmacology",
                            "Oral Diagnosis/Medicine",
                            "Oral Surgery",
                            "Other"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 20))) #+
  #coord_flip()
p

```

##Hours
###How many hours of training in principles of antibiotic use do you think you have received to date in your dental education?

```{r}
hours <- data.frame(table(students$hours_training, useNA = "ifany"))
names(hours) <- c("Hours", "Count")

p<-ggplot(data=hours, aes(x = Hours, y = Count)) +
  ylim(0,76) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("0-10",
                            "11-20",
                            "21-40",
                            "41-60",
                            "61+"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p
```

##Teaching format
###What kind of teaching format has been used during your education on antibiotics? [Choose all that apply]
```{r}
teaching <- students[,grep("teaching_format___",names(students))]
teaching <- teaching[,1:6]
teaching <- data.frame(colSums(teaching))

p<-ggplot(data=teaching, aes(x = rownames(teaching), y = colSums.teaching.)) +
  ylim(0,190) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  ylab("Count")+
  xlab("Department")+ 
  geom_text(aes(label=colSums.teaching.), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("Lectures",
                            "Clinical Vignettes/Case Discussions",
                            "E-learning",
                            "Web-based learning platform",
                            "Direct patient care",
                            "Other"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 50))) #+
  #coord_flip()
p

```

##Helpful
###Which of the teaching formats do you feel were most helpful in your education and understanding related to antibiotics? [Please select up to 3]

```{r}
helpful <- students[,grep("format_helpful___",names(students))]
helpful <- helpful[,1:8]
helpful <- data.frame(colSums(helpful))

p<-ggplot(data=helpful, aes(x = rownames(helpful), y = colSums.helpful.)) +
  ylim(0,152) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  ylab("Count")+
  xlab("Department")+ 
  geom_text(aes(label=colSums.helpful.), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("Lectures",
                            "Clinical Vignettes/Case Discussions",
                            "E-learning",
                            "Web-based learning platform",
                            "Direct patient care",
                            "Specialty Rotations",
                            "External Rotations",
                            "Other"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 50))) #+
  #coord_flip()
p

```

##Guidelines
###Do you currently have established clinical guidelines for antibiotic prescribing within any of the following disciplines at your dental school? [Choose all that apply]

```{r}
guides <- students[,grep("guidelines___",names(students))]
guides <- guides[,1:9]
guides <- data.frame(colSums(guides))

p<-ggplot(data=guides, aes(x = rownames(guides), y = colSums.guides.)) +
  ylim(0,109) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  ylab("Count")+
  xlab("Department")+ 
  geom_text(aes(label=colSums.guides.), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("Endodontics",
                            "General Practice",
                            "Oral Diagnosis/Medicine",
                            "Oral Surgery",
                            "Pediatrics",
                            "Periodontics",
                            "Institution-wide",
                            "Other",
                            "I don't know"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 20))) #+
  #coord_flip()
p

```

##Greatest Impact
###Who/what has had the greatest impact on your decision of when and how to prescribe antibiotics?[Please select up to 3]

```{r}
impact <- students[,grep("greatest_impact___",names(students))]
impact <- impact[,1:7]
impact <- data.frame(colSums(impact))

p<-ggplot(data=impact, aes(x = rownames(impact), y = colSums.impact.)) +
  ylim(0,170) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  ylab("Count")+
  xlab("Department")+ 
  geom_text(aes(label=colSums.impact.), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("Full-time faculty in clinic",
                            "Part-time faculty in clinic",
                            "Student peers",
                            "Didactic courses",
                            "Personal experience",
                            "Personal research/investigation",
                            "Other"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 40))) #+
  #coord_flip()
p

```


##Confidence
###With your current level of understanding, how confident would you feel in the following scenarios when prescribing an antibiotic by yourself? Please use the scale provided to answer with 0 indicating not at all confident and 100 indicating very confident.

```{r}
vars <- c("record_id","infection","choosing","dose","duration","demand")
confidence <- students[,which(names(students) %in% vars)]

#infection
#summary(confidence$infection)
infection <- data.frame(Minimum = as.vector(summary(confidence$infection))[1],
                  "First Quartile"= as.vector(summary(confidence$infection))[2],
                  Median= as.vector(summary(confidence$infection))[3],
                  Mean= as.vector(summary(confidence$infection))[4],
                  SD = sd(na.omit(confidence$infection)),
                  "Third Quartile"= as.vector(summary(confidence$infection))[5],
                  Maximum= as.vector(summary(confidence$infection))[6],
                  Missing=length(which(is.na(confidence$infection))))
infection <- round(infection, 2)
kable(infection)


#choosing
#summary(confidence$choosing)
choosing <- data.frame(Minimum = as.vector(summary(confidence$choosing))[1],
                  "First Quartile"= as.vector(summary(confidence$choosing))[2],
                  Median= as.vector(summary(confidence$choosing))[3],
                  Mean= as.vector(summary(confidence$choosing))[4],
                  SD = sd(na.omit(confidence$choosing)),
                  "Third Quartile"= as.vector(summary(confidence$choosing))[5],
                  Maximum= as.vector(summary(confidence$choosing))[6],
                  Missing=length(which(is.na(confidence$choosing))))
choosing <- round(choosing, 2)
kable(choosing)


#dose
#summary(confidence$dose)
dose <- data.frame(Minimum = as.vector(summary(confidence$dose))[1],
                  "First Quartile"= as.vector(summary(confidence$dose))[2],
                  Median= as.vector(summary(confidence$dose))[3],
                  Mean= as.vector(summary(confidence$dose))[4],
                  SD = sd(na.omit(confidence$dose)),
                  "Third Quartile"= as.vector(summary(confidence$dose))[5],
                  Maximum= as.vector(summary(confidence$dose))[6],
                  Missing=length(which(is.na(confidence$dose))))
dose <- round(dose, 2)
kable(dose)


#duration
#summary(confidence$duration)
duration <- data.frame(Minimum = as.vector(summary(confidence$duration))[1],
                  "First Quartile"= as.vector(summary(confidence$duration))[2],
                  Median= as.vector(summary(confidence$duration))[3],
                  Mean= as.vector(summary(confidence$duration))[4],
                  SD = sd(na.omit(confidence$duration)),
                  "Third Quartile"= as.vector(summary(confidence$duration))[5],
                  Maximum= as.vector(summary(confidence$duration))[6],
                  Missing=length(which(is.na(confidence$duration))))
duration <- round(duration, 2)
kable(duration)


#demand
#summary(confidence$demand)
demand <- data.frame(Minimum = as.vector(summary(confidence$demand))[1],
                  "First Quartile"= as.vector(summary(confidence$demand))[2],
                  Median= as.vector(summary(confidence$demand))[3],
                  Mean= as.vector(summary(confidence$demand))[4],
                  SD = sd(na.omit(confidence$demand)),
                  "Third Quartile"= as.vector(summary(confidence$demand))[5],
                  Maximum= as.vector(summary(confidence$demand))[6],
                  Missing=length(which(is.na(confidence$demand))))
demand <- round(demand, 2)
kable(demand)
```


##More education
###Would you like more education on antibiotic selection and indications at your dental school?

```{r}

moreed <- data.frame(table(students$more_educ, useNA = "ifany"))
names(moreed) <- c("Response", "Count")

p<-ggplot(data=moreed, aes(x = Response, y = Count)) +
  ylim(0,135) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No",
                            "Yes",
                            "Adequate training"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p

```


##Unethical
###Do you believe that prescribing antibiotics when they are not indicated is professionally unethical?

```{r}
unethic <- data.frame(table(students$unethical, useNA = "ifany"))
names(unethic) <- c("Response", "Count")

p<-ggplot(data=unethic, aes(x = Response, y = Count)) +
  ylim(0,157) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No",
                            "Yes",
                            "Unsure"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p

```


##Resist
###Do you think that antibiotic resistance is a national problem?

```{r}

resist <- data.frame(table(students$national_problem, useNA = "ifany"))
names(resist) <- c("Response", "Count")

p<-ggplot(data=resist, aes(x = Response, y = Count)) +
  ylim(0,178) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No",
                            "Yes",
                            "Unsure"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p


```

##Scenarios
###The following scenarios are potential causes for resistance; please identify which, in your opinion, are the most or least important contributors to resistance?

```{r}
vars <- c("num_rx","broad_spec","long_duration","dose_low","livestock","hand_wash","development","not_warranted","diagnostic_tools","wrong_anti","non_compliance" )

scenarios <- students[,which(names(students) %in% vars)]
title <- c("Too many antibiotic prescriptions",
           "Too many broad-spectrum antibiotics used",
           "Too long of a duration of antibiotic treatment",
           "Dosing of antibiotics are too low",
           "Excessive use of antibiotics in livestock",
           "Poor hand hygiene",
           "Lack of antibiotics being developed",
           "Prescribing antibiotics when the situation doesn't warrant its use",
           "Lack of effective diagnostic tools",
           "Using the wrong antibiotic for the situation",
           "Patient non-compliance or self-medicating with antibiotic treatment")

  
  df1 <- data.frame(table(scenarios[,1], useNA = "ifany"))
  names(df1) <- c("Response", "Count")
  
  p <- ggplot(data=df1, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[1])
  p
  
##########################
  
df2 <- data.frame(table(scenarios[,2], useNA = "ifany"))
  names(df2) <- c("Response", "Count")
  
  p <- ggplot(data=df2, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[2])
  p

  ##########################
  
df3 <- data.frame(table(scenarios[,3], useNA = "ifany"))
  names(df3) <- c("Response", "Count")
  
  p <- ggplot(data=df3, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[3])
  p

  ##########################
  
df4 <- data.frame(table(scenarios[,4], useNA = "ifany"))
  names(df4) <- c("Response", "Count")
  
  p <- ggplot(data=df4, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[4])
  p

  ##########################
  
df5 <- data.frame(table(scenarios[,5], useNA = "ifany"))
  names(df5) <- c("Response", "Count")
  
  p <- ggplot(data=df5, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[5])
  p

  ##########################
  
df6 <- data.frame(table(scenarios[,6], useNA = "ifany"))
  names(df6) <- c("Response", "Count")
  
  p <- ggplot(data=df6, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[6])
  p

  ##########################
  
df7 <- data.frame(table(scenarios[,7], useNA = "ifany"))
  names(df7) <- c("Response", "Count")
  
  p <- ggplot(data=df7, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[7])
  p

  ##########################
  
  df8 <- data.frame(table(scenarios[,8], useNA = "ifany"))
  names(df8) <- c("Response", "Count")
  df8 <- rbind.data.frame(data.frame(Response="0", Count=0), df8)
  
  p <- ggplot(data=df8, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[8])
  p

  ##########################
  
  df9 <- data.frame(table(scenarios[,9], useNA = "ifany"))
  names(df9) <- c("Response", "Count")
  #df <- rbind.data.frame(data.frame(Response="0", Count=0), df)
  
  p <- ggplot(data=df9, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[9])
  p

  ##########################
  
  df10 <- data.frame(table(scenarios[,10], useNA = "ifany"))
  names(df10) <- c("Response", "Count")
  #df <- rbind.data.frame(data.frame(Response="0", Count=0), df)
  
  p <- ggplot(data=df10, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[10])
  p
  
  ##########################
  
  df11 <- data.frame(table(scenarios[,11], useNA = "ifany"))
  names(df11) <- c("Response", "Count")
  df11 <- rbind.data.frame(data.frame(Response="0", Count=0), df11)
  
  p <- ggplot(data=df11, aes(x = Response, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("No Impact",
                            "Some Impact",
                            "Great Impact"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15)))+
    ggtitle(title[11])
  p


  
```


##Unnecessary
###What percentage of antibiotic prescriptions within dentistry do you think are estimated to be unnecessary or inappropriate?

```{r}

unnec <- data.frame(table(students$percent_unnecessary, useNA = "ifany"))
names(unnec) <- c("Response", "Count")

p<-ggplot(data=unnec, aes(x = Response, y = Count)) +
  ylim(0,69) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  scale_x_discrete(labels=c("<1%",
                            "1-20%",
                            "21-40%",
                            "41-60%",
                            "61-80%",
                            "81-100%"))+
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p


```


##Consequences
###In a 10-year perspective, do you think the consequences of antibiotic resistance will affect your future work when caring for patients with dental infections?

```{r}
conseq <- data.frame(table(students$future_effect, useNA = "ifany"))
names(conseq) <- c("Response", "Count")
conseq <- rbind.data.frame(data.frame(Response="1",Count=0), conseq)
conseq$Response <- as.factor(conseq$Response)

levels(conseq$Response) <- c("Not at all",
                          "Rarely",
                          "Occationally",
                          "Often",
                          "Very Often")

p<-ggplot(data=conseq, aes(x = Response, y = Count)) +
  ylim(0,81) +
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p

```


##Healthcare
###If so, what do you expect will be the greatest problem within healthcare?

```{r}
health <- data.frame(table(students$greatest_prob, useNA = "ifany"))
names(health) <- c("Response", "Count")
health <- rbind.data.frame(health, data.frame(Response="6",Count=0))
health$Response <- as.factor(health$Response)

levels(health$Response) <- c("More expensive treatment",
                          "Fewer treatment alternatives",
                          "Increased morbidity due to untreatable bacterial infections",
                          "Increased spread of communicable diseases due to untreatable infections",
                          "I don't know",
                          "Other")

p<-ggplot(data=health, aes(x = stringr::str_wrap(Response, 15), y = Count)) +
  ylim(0,74)+
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  xlab("Problems in healthcare")
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p

```


##Importance
###On a scale of 0-100, with 0 being the least and 100 being the most, how important do you perceive this topic to be within dental education?

```{r}

import <- data.frame(Minimum = as.vector(summary(students$importance))[1],
                  "First Quartile"= as.vector(summary(students$importance))[2],
                  Median= as.vector(summary(students$importance))[3],
                  Mean= as.vector(summary(students$importance))[4],
                  SD=sd(na.omit(students$importance)),
                  "Third Quartile"= as.vector(summary(students$importance))[5],
                  Maximum= as.vector(summary(students$importance))[6],
                  Missing=length(which(is.na(students$importance))))
import <- round(import, 2)
#datatable(import)
kable(import)
```


##Stewardship
###Are you familiar with the term "antimicrobial stewardship"?

```{r}
steward <- data.frame(table(students$antimicrobial_steward, useNA = "ifany"))
names(steward) <- c("Response", "Count")
steward$Response <- factor(steward$Response)
levels(steward$Response) <- c("Very familiar",
                          "Familiar",
                          "Not Familiar",
                          "Not at all familiar")

p<-ggplot(data=steward, aes(x = Response, y = Count)) +
  ylim(0,107)+
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p

```


##Important Role
###Dentistry should play an important role in reducing antimicrobial resistance

```{r}

role <- data.frame(table(students$should_role, useNA = "ifany"))
names(role) <- c("Response", "Count")
role <- rbind.data.frame(data.frame(Response="-2",Count=0),
                         data.frame(Response="-1",Count=0),
                         role)
role$Response <- factor(role$Response)
levels(role$Response) = c("Strongly Disagree",
                          "Disagree",
                          "Neutral",
                          "Agree",
                          "Strongly Agree")

p<-ggplot(data=role, aes(x = Response, y = Count)) +
  ylim(0,91)+
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p


```


##Self Role
###How interested are you in playing a role in this improvement through better self-monitoring and antibiotic stewardship? Please use the scale provided to answer with 0 indicating not at all and 100 indicating very interested.

```{r}
self <- data.frame(Minimum = as.vector(summary(students$self_role))[1],
                  "First Quartile"= as.vector(summary(students$self_role))[2],
                  Median= as.vector(summary(students$self_role))[3],
                  Mean= as.vector(summary(students$self_role))[4],
                  SD=sd(na.omit(students$self_role)),
                  "Third Quartile"= as.vector(summary(students$self_role))[5],
                  Maximum= as.vector(summary(students$self_role))[6],
                  Missing=length(which(is.na(students$self_role))))
self <- round(self, 2)
#datatable(self)
kable(self)
```


##Contribution
###Please indicate your agreement with the following sentence: Dental students can contribute in reducing and controlling antibiotic resistance?

```{r}

contribute <- data.frame(table(students$students_contribute, useNA = "ifany"))
names(contribute) <- c("Response", "Count")
contribute$Response <- factor(contribute$Response)
levels(contribute$Response) <- c("Strongly Disagree",
                          "Disagree",
                          "Neutral",
                          "Agree",
                          "Strongly Agree")

p<-ggplot(data=contribute, aes(x = Response, y = Count)) +
  ylim(0,89)+
  geom_bar(stat="identity", fill="steelblue")+
  #scale_fill_brewer(palette="Blues") +
  geom_text(aes(label=Count), vjust=-.5, color="black", size=5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 15))) #+
  #coord_flip()
p



```

